On the uniqueness and stability of dictionaries for sparse representation of noisy signals

### 2017-11-28 manuscripts/PNAS/second review/resub/chazthm_pnas_resub.tex
lemma 4 more clear

Finally, substituting this into \eqref{f} and rearranging produces \eqref{DTILeq} after substituting $\xi(\mathcal{V})$ for $z$.
\end{proof}
\begin{lemma}\label{NonEmptyLemma} 
Fix an $r$-regular hypergraph $\mathcal{H} \subseteq 2^{[m]}$ satisfying the SIP. If the map $\pi: \mathcal{H} \to 2^{[\overline m]}$ has $\sum_{S \in \mathcal{H}} |\pi(S)| \geq \sum_{S \in \mathcal{H}} |S|$ and:
\begin{align}\label{cond}
	|\cap \pi(\mathcal{G})| \leq |\cap \mathcal{G} |,\ \ \   \text{for } \mathcal{G} \in {\mathcal{H} \choose r} \cup {\mathcal{H} \choose r+1},
\end{align}
%
then $\overline m \geq m$, and if $\overline m < mr / (r-1)$ then the map $i \mapsto \cap \pi(\sigma(i))$ is an injective map to $[\overline m]$ from some $J \subseteq [m]$ of size $\overline m - r(\overline m - m)$. %In particular, if $\overline m = m$ then $\pi$ is induced by a permutation on $[m]$.
\end{lemma}
\begin{proof}
Consider the set: $T_1 := \{(i, S): i \in \pi(S), S \in \mathcal{H}\}$, which number $|T_1| = \sum_{S \in \mathcal{H}} |\pi(S)| \geq \sum_{S \in \mathcal{H}} |S| = \sum_{i \in [m]} \deg_\mathcal{H}(i) = mr$. Note that \eqref{cond} implies $|T_1| \leq \overline m r$, since otherwise pigeonholing the elements of $T_1$ with respect to their possible first indices $[\overline m]$ would imply $\deg_\mathcal{H}(i) > r$ for some $i \in [m]$. Thus, $\overline m \geq m$.

If $\overline m < mr / (r-1)$, then $p := \overline m - r( \overline m - m)$ is positive and $|T_1| \geq \overline m (r - 1) + p$. Pigeonholing $T_1$ into $[\overline m]$ again, there must be $r$ elements of $T_1$ sharing the same first index. By \eqref{cond}, the intersection of the set $\mathcal{G}_1$ of their second indices is nonempty; hence, $|\cap \mathcal{G}_1| = 1$ by $r$-regularity and the SIP. Since $\cap \pi(\mathcal{G}_1)$ is nonempty, applying \eqref{cond} again gives $\cap \pi(\mathcal{G}_1) = \{i_1\}$ for some $i_1 \in [\overline m]$. If $p=1$, then we are done. Otherwise, define $T_2 := T_1 \setminus \{(i,S) \in T_1: i = i_1\}$, which contains $|T_2| = |T_1| - r \geq (\overline m - 1)(r-1) + (p-1)$ ordered pairs having $\overline m - 1$ distinct first indices. Repeating the above arguments produces a (necessarily, by $r$-regularity and the SIP) distinct $\mathcal{G}_2 \in {\mathcal{H} \choose r}$ and corresponding $i_2 \in [\overline m]$. Finally, iterating this $p$ times in total yields the set of singletons \mbox{$J = \{\cap \mathcal{G}_1, \ldots, \cap \mathcal{G}_p\} \subseteq [m]$}.
\end{proof}

>>>>

Finally, substituting this into \eqref{f} and rearranging produces \eqref{DTILeq} after substituting $\xi(\mathcal{V})$ for $z$.
\end{proof}
\begin{lemma}\label{NonEmptyLemma} 
Fix an $r$-regular hypergraph $\mathcal{H} \subseteq 2^{[m]}$ satisfying the SIP. If the map $\pi: \mathcal{H} \to 2^{[\overline m]}$ has $\sum_{S \in \mathcal{H}} |\pi(S)| \geq \sum_{S \in \mathcal{H}} |S|$ and:
\begin{align}\label{cond}
	|\cap \pi(\mathcal{G})| \leq |\cap \mathcal{G} |,\ \ \   \text{for } \mathcal{G} \in {\mathcal{H} \choose r} \cup {\mathcal{H} \choose r+1},
\end{align}
%
then $\overline m \geq m$, and if $\overline m < mr / (r-1)$ then the map $i \mapsto \cap \pi(\sigma(i))$ is an injective map to $[\overline m]$ from some $J \subseteq [m]$ of size $\overline m - r(\overline m - m)$. %In particular, if $\overline m = m$ then $\pi$ is induced by a permutation on $[m]$.
\end{lemma}
\begin{proof}
Consider the set: $T_1 := \{(i, S): i \in \pi(S), S \in \mathcal{H}\}$, which numbers $|T_1| = \sum_{S \in \mathcal{H}} |\pi(S)| \geq \sum_{S \in \mathcal{H}} |S| = \sum_{i \in [m]} \deg_\mathcal{H}(i) = mr$. Note that $|T_1| \leq \overline m r$ by \eqref{cond}, since otherwise pigeonholing the elements of $T_1$ with respect to their possible first indices $[\overline m]$ would imply $\deg_\mathcal{H}(i) \geq r$ for some $i \in [m]$. Thus, $\overline m \geq m$.

Suppose $\overline m (r-1) < mr$, so that $|T_1| \geq mr = \overline m (r - 1) + p$ for positive $p := mr - \overline m (r-1)$. Pigeonholing $T_1$ into $[\overline m]$ again, there must be at least $r$ elements of $T_1$ that share a first index. Let $i_1 \in [\overline m]$ be such an index and note that, in fact, no more than $r$ elements of $T_1$ can have $i_1$ as a first index; otherwise, the set $\mathcal{G}_1$ of their second indices would contain $r+1$ elements with a non-empty intersection by \eqref{cond}, contradicting $r$-regularity of $\mathcal{H}$. Thus, $|\mathcal{G}_1| = r$, and \eqref{cond} implies $|\cap \mathcal{G}_1| = 1$ by $r$-regularity and the SIP. If $p=1$, then we are done. Otherwise, define $T_2 := T_1 \setminus \{(i,S) \in T_1: i = i_1\}$, which contains $|T_2| = |T_1| - r \geq (\overline m - 1)(r-1) + (p-1)$ ordered pairs having $\overline m - 1$ distinct first indices. Repeating the above arguments thus produces a distinct $i_2 \in [\overline m]$ and $\mathcal{G}_2 \in {\mathcal{H} \choose r}$ with (necessarily, by $r$-regularity and the SIP) distinct singleton $\cap \mathcal{G}_2 \in [m]$. Finally, iterating this $p$ times in total yields the set of singletons \mbox{$J = \{\cap \mathcal{G}_1, \ldots, \cap \mathcal{G}_p\}$}.
\end{proof}
